Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-02-14 ms/Accessory/Wenk-Accessory-SI.Rnw
few more changes to Supplementary Information file

Describe contents of csv files attached

List of data files.

What is measured by individual and species

- for flower parts, the default is at the species level unless the actual piece was collected; Plant parts that were collected on an individual is recorded in the file flowerParts
- all reproductive output is measured at the individual

Census

@@

\section{Details about input files}
floweringCategories
This file contains a matrix of plant parts (rows) by species (columns). For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet. Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.

@@

@@

Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field. For some reproductive parts a simple count is pracical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure. For species that form cones, the cones can be notably different in size and each cone's dimensions must be recorded.

@@

For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
As the reproductive cycle progresses, tissue parts were repeatedly split into two (or more) parts. For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma. As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts. This is shown in the map for each species.

>>>>

@@

\subsection{investment categories by species}
List for each species of reproductive tissue types included in each of the investment categories
<<echo=FALSE,results='asis'>>=
  @@@("../../data/accessoryParts.yml")
@

\section{Details about input files}
List of data files.

floweringCategories
This file contains a matrix of plant parts (rows) by species (columns). For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet. Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.

@@

\subsection{Overview of plant maps}

For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
As the reproductive cycle progresses, tissue parts were repeatedly split into two (or more) parts. For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma. As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts. Along the developmental trajectory, various reproductive tissues are designated as reaching their final development stage, the point in the reproductive cycle where they no longer increase in mass. For some tissues, such as petals, final development is reached long before a mature seed forms, while other tissues, such as the seed and seedpod do not reach final development until the end of the developmental trajectory.

Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development. The central development axis terminates with the formation of a mature seed, while side branches end in fully developed tissues (such as petals, calyx, pedicel) and aborted tissues (aborted seeds, aborted fruit) at the point where they cease to increase in mass. The developmental flowchart for each species is shown in the maps in the next section.

\subsection{How the census is completed for each part}

The count of each reproductive tissue type was determined for each individual at each census time. For some reproductive parts a simple count is practical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure. For species that form cones, the cones can be notably different in size and each cone's dimensions must be recorded throughout development.

\subsection{How parts weights are determined}

For all plant parts, a sample of the representative part was collected on other individuals in the population to obtain a mean tissue mass. For plant parts that vary considerably in size, such as cones, the mass of parts of different sizes was measured and a regression of mass per length or mass per volume was established. The data file flowerCategories indicates, for each reproductive tissue type, for each species, what method was used to determine the mass of the plant part.

For some individuals, actual reproductive parts were collected. This includes any reproductive parts of the plants at the time of harvest, including both current reproductive tissues and previously mature woody fruits still attached to the branches. In additional some seeds were collected once mature, but before they were dispersed. Whenever actual reproductive parts were collected from an individual, the unit mass of these structures was used instead of the population mean.

\subsection{R scripts used to calculate reproductive investment}

@@

Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.

@@
